A component-based DSL for multi-stencil programs

### 2015-07-21 WOLFHPC15/article/related.tex
wolfhpc15 21_07

>>>>

On the other hand, the work presented in this paper does not propose to optimize and parallelize a single stencil code for shared memory machines, GPGPUs or many-core architectures. The MS language and the MSC compiler produce a coarse-grain parallel structure of the overall simulation which could be combined to existing stencil compilers.
